\documentclass[a4paper,15pt]{article}
\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

% Custom section formatting
\titleformat{\section}{\large\bfseries}{\thesection}{0.5em}{}[\titlerule]

% Compact itemize
\setlist[itemize]{leftmargin=0.5em, itemsep=1pt, topsep=1pt}

% Reduce spacing between sections
\titlespacing{\section}{4pt}{*1}{*1}

% Reduce spacing within lists
\setlength{\parskip}{2pt}
\setlength{\parsep}{2pt}
\setlength{\itemsep}{2pt}
% Reduce font size for content
\renewcommand{\large}{\fontsize{11pt}{13pt}\selectfont}

\begin{document}

\pagestyle{empty}

\begin{center}
    \textbf{\LARGE Yashas Chandrashekar} \\
    \vspace{1mm}
    +91 9739750742 | yashaschandrashek4r@gmail.com | \href{https://linkedin.com/in/yashaschandrashekar}{\underline{LinkedIn}} | \href{https://github.com/yashasc2k1}{\underline{GitHub}} | \href{https://yashasc2k1.github.io/YashasChandrashekar/}{\underline{Portfolio}} | \href{https://leetcode.com/YashasC/}{\underline{LeetCode}}
\end{center}

% Skills
\section*{Skills}
\textbf{Programming Languages:}
Golang, Java, Python, C, JavaScript, PHP, HTML, CSS \LaTeX \\
% \textbf{Web Technologies:}
% Apache2, Ngrok, Telebit \\
\textbf{Cloud Technologies:}
AWS (Amazon Web Services), Firebase, GCS \\
\textbf{Databases:}
MySQL, PostgreSQL, MongoDB, MariaDB\\
\textbf{IDE:}
IntelliJ IDEA, Atom, Visual Studio Code

% Experience
\section*{Experience}
\textbf{Backend Developer} \\
Zino Technologies, Bengaluru, Karnataka \hfill January 2024 - Present
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Developed and integrated industry-standard inventory modules into the low-code platform to meet diverse business needs.
    \item Enhanced platform's data management capabilities integrating PostgreSQL and RDBMS databases.
    \item Built an in-app chat system for seamless communication within applications.
    \item Streamlined team collaboration by integrating Slack into workflows.
    \item Implemented Razorpay integration, offering customizable payment solutions for platform applications.
    \item Delivered real-time notifications through Firebase Cloud Messaging (FCM), ensuring timely updates for users.
    \item Added Excel import/export and document conversion functionality using Golang's `excelize` package.

    \item \textbf{AI-Driven Accomplishments:}
    \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Designed AI-powered state machine workflows for dynamically generating workflows based on descriptive prompts.
        \item Built AI-driven activity execution, allowing users to execute activities through natural language prompts.
        \item Integrated VAPI voice agents for automated voice interactions, enhancing user engagement.
        \item Leveraged AWS Textract and OpenAI for OCR capabilities, automating text extraction and processing.
        \item Developed AI-based tools for data analysis, insights extraction, and comprehensive report generation.
        \item Created an OpenAI-powered assistant for automating form-filling and activity identification based on user instructions.
        \item Automated form generation via AI, enabling users to create functional forms using descriptive prompts.
    \end{itemize}
\end{itemize}


% Education
\section*{Education}
\textbf{Computer Science and Engineering} \\
Reva University, Bengaluru, Karnataka \hfill August 2019 - August 2023 \\
\textit{CGPA: 8.74 (First class with Distinction)}

% Personal Projects
\section*{Personal Projects}

\textbf{OpinionBox} \hfill 2023 \\
\textit{Technologies}: HTML, CSS, JavaScript, BootStrap, PHP, Apache2, MariaDB, Linux, Telebit \\
\textit{Description}: Developed a web platform enabling peers to anonymously share opinions and rate classmates on a scale of 1 to 10, fostering constructive feedback within the academic community. This website was hosted live for over 3 days, resulting in over 50 registered users. \\
\textit{\href{https://github.com/yashasc2k1/OpinionBox}{\underline{Project Link}}}

\textbf{Sudoku Solver} \hfill 2023 \\
\textit{Technologies}: HTML, CSS, JavaScript \\
\textit{Description}: Built a Sudoku Solver web app for interactive puzzle solving, automating cell-fill functionality upon user request. Demonstrated algorithmic problem-solving and user-centric design. \\
\textit{\href{https://yashasc2k1.github.io/SudokuSolver}{\underline{Project Link}}}

\textbf{Knee OsteoArthritis Detection using CNN} (Team Project) \hfill 2022-2023 \\
\textit{Technologies}: Python, CNN, HTML, CSS, JavaScript \\
\textit{Description}: Developed a CNN-based system for knee osteoarthritis prediction using X-ray images. The model evaluates the severity on a 5-scale metric when users upload their knee X-ray images. Recognized with the Best Outgoing Project award at Reva University. \\
\textit{\href{https://github.com/yashasc2k1/KneeOsteoArthritis}{\underline{Project Link}}} \textit{\href{https://www.ijraset.com/research-paper/knee-osteoarthritis-detection-and-severity-prediction}{\underline{Research Paper Link}}}

% \textbf{Personal Portfolio} \hfill 2023 \\
% \textit{Technologies}: HTML, CSS, JavaScript \\
% \textit{Description}: In-progress portfolio website development, showcasing skills and projects. \\
% \textit{\href{https://yashasc2k1.github.io/YashasChandrashekar/}{\underline{Project Link}}}

% % Academic Projects
% \section*{Academic Projects}
% \textbf{Knee OsteoArthritis Detection using CNN} (Team Project) \hfill 2022-2023 \\
% \textit{Technologies}: Python, CNN, HTML, CSS, JavaScript \\
% \textit{Description}: Developed a CNN-based system for knee osteoarthritis prediction using X-ray images. The model evaluates the severity on a 5-scale metric when users upload their knee X-ray images. Recognized with the Best Outgoing Project award at Reva University. \\
% \textit{\href{https://github.com/yashasc2k1/KneeOsteoArthritis}{\underline{Project Link}}} \textit{\href{https://www.ijraset.com/research-paper/knee-osteoarthritis-detection-and-severity-prediction}{\underline{Research Paper Link}}}

% \textbf{Hospital DataBase} \hfill 2021 \\
% \textit{Technologies}: HTML, CSS, PHP, MariaDB, MySQL, AWS, Linux, Apache2 \\
% \textit{Description}: Created a streamlined Hospital Database Management system enabling user registration through a user-friendly form. Admins can easily access and view details of registered patients, enhancing the efficiency of healthcare data management. \\
% \textit{\href{https://github.com/yashasc2k1/webfilesrr}{\underline{Project Link}}}

Certifications
\section*{Certifications}
\begin{tabular}{@{}ll@{}}
    \textbf{Database Management System}                                                                                            &
    \textbf{Learning Data Analytics}                                                                                                 \\
    NPTEL, 2023                                                                                                                    &
    NPTEL, 2022                                                                                                                      \\
    \textit{\href{https://internalapp.nptel.ac.in/noc/Ecertificate/?q=NPTEL23CS41S1422070903136655}{\underline{Certificate Link}}} &
    \textit{\href{https://archive.nptel.ac.in/noc/Ecertificate/?q=NPTEL22GE26S3394039710215318}{\underline{Certificate Link}}}
\end{tabular}

\end{document}

